The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$

### 2015-05-15 formalwriteup.tex
Change section title
Reword intro

Our techniques are inspired by taking characteristic $p$ analogues of results about Cherednik algebras in characteristic $0$.  In particular, our explicit expression for generators of the maximal ideal was obtained by converting expressions containing complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.  While we restrict our study to type $A$ in this paper, we view this problem as a test case this philosophy and believe it may admit wider application.

>>>>

Our techniques are inspired by taking characteristic $p$ analogues of results about Cherednik algebras in characteristic $0$.  In particular, our explicit expression for generators of the maximal ideal was obtained by converting expressions containing complex residues to equivalent expressions dealing only with formal power series which may be interpreted in characteristic $p$.  While we restrict our present study to the polynomial representation in type $A$, we view this problem as a test case for this philosophy and believe it may admit wider application.
